---
title: "Analyze bursts"
output: html_notebook
---

Demonstrates burst analysis on a sample data from a simple burster (modified Poisson process): an ON-OFF switch with events firing in the ON state. Transition rates are kON = kOFF = 0.1 [1/T], kProd = 10 [1/T]. Thus, on average, there are 100 events per ON state. The ON and OFF states last, on average, 10 time units each.

```{r}
require(ggplot2)
require(dplyr)
source('auxfn.R')
source('calcBurstSzFn.R')

# read example data
df = read.csv('../example-data-1/output1.prel', header = F)

# calculate burst size function
df.phi=calcBurstSzFn(df$V1, 100, 1/2)

```

## Plot of burst size function.

```{r}
ggplot(df.phi, aes(x=t, y=b)) +
  geom_line() +
  xlab("\nthreshold length [T]") +
  ylab("burst size\n") +
  myGGtheme

```

## Burst size 
Calculated at taux, which lies in the middle between two inflection points, tau1 and tau2:

```{r}
tx = 0.8
f.inter = function(x) splinefun(df.phi$t, df.phi$b, method='monoH.FC')(x)
f.inter(tx)

```

## Burst significance

Formula: 1 - tau2/tau1. Requires calculation of two inflection points of the burst size function. Here, we assume that tau2 is at tau=1.5 and tau1 at tau=0.5.

```{r}
1 - f.inter(0.5)/f.inter(1.5)
```


## Burst duration
τβ, is the mean inter-arrival time within a burst. Calculate by averaging over intervals lower than τX.

```{r}
v.sub = df$V1[df$V1 > 0 & df$V1 < tx]
mean(v.sub)
```

## Burstiness
See definition in https://arxiv.org/pdf/1604.01125.pdf

B has the value of −1 for regular time series as σ = 0, and 0 for Poissonian or random time series as σ = μ. Finally, the value of B approaches 1 for extremely bursty time series as σ → ∞ for finite μ. 

```{r}
(sd(df$V1) - mean(df$V1))/(sd(df$V1) + mean(df$V1))
```

